---
title: "Heroin Overdoses in the City of Mesa"
author: "Aidan Rhianne & Chris Michael"
date: "December 2nd, 2022"
output: 
  html_document:
    df_print: paged
    code_folding: hide
    fig_caption: yes
    toc: true
    toc_float: true
    theme: readable
---

------------------------------------------------------------------------

# A. Introduction 

------------------------------------------------------------------------

### The Purpose of Predictive Overdoses

Aims and purposes

------------------------------------------------------------------------

# B. Set-Up

------------------------------------------------------------------------

### I. Installing Packages 

```{r Setup, results='hide', warning = FALSE, message = FALSE}
library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat)
library(raster)
library(spdep)
library(FNN)
library(grid)
library(gridExtra)
library(RColorBrewer)
library(knitr)
library(kableExtra)
library(tidycensus)
library(classInt)   
library(kableExtra)
library(RColorBrewer)
library(hrbrthemes)
library(ggthemes)
library(ggplot2)
library(plotly)
library(scales)
library(extrafont)
library(basetheme)
library(RColorBrewer)
library(lemon)
library(data.table)
library(GGally)
require(gridExtra)
library(ggalt)
library(rgeos)
library(sp)
library(smoothr)
library(rgdal)
library(rgeos)
library(maptools)
library(ggmap)
library(scales) 
library(ggeasy)
library("wesanderson")
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(ggcorrplot) 
library(corrr)      
library(kableExtra)
library(jtools)     
library(ggstance) 
library(ggpubr)    
library(broom.mixed) 
library(tab)
library(sjPlot)
library(plotly)
library(stargazer)
library(pscl)
library(plotROC)
library(pROC)
library(lubridate)

col <- wes_palette("Zissou1")
col5 <- colorRampPalette(col)(5)
col6 <- colorRampPalette(col)(6)
col7 <- colorRampPalette(col)(7)
col8 <- colorRampPalette(col)(8)
col10 <- colorRampPalette(col)(10)
col22 <- colorRampPalette(col)(22)
col29 <- colorRampPalette(col)(29)
col96 <- colorRampPalette(col)(96)

options(scipen = 999)
options(tigris_class = "sf")

root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

```


We started creating the markdown by installing the required packages and loading them into the library. Some of the mainly used packages are `tidyverse`, `tidycensus`, and `dplyr`. The final deliverable for this homework is an RMarkdown file with the required plots and tables, knitted to a HTML document. <br/><br/>

------------------------------------------------------------------------

# C. City of Mesa Data

------------------------------------------------------------------------

### I. Reading the Data 

Pulled data from Mesa, AZ Open Data


```{r set working directory,}
# Aidan WD
#setwd("C:/Users/aidan/OneDrive/Documents/GitHub/Final")

# Chris WD
setwd("C:/Users/Chris Michael/Desktop/UPenn/Fall 2022/508/MUSA_508_Lab-main/MUSA_508_Lab-main/Final")

```

```{r Overdose data, results='hide', warning = FALSE, message = FALSE, cache = TRUE}

MesaHero <- read.csv("C:/Users/Chris Michael/Desktop/UPenn/Fall 2022/508/MUSA_508_Lab-main/MUSA_508_Lab-main/Final/Fire_and_Medical_Opioid_Overdose_Incidents.csv")

plot(MesaHero)

```

### II. Exploring the Data
